Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-03-09 rmd/manuscript.Rmd
Update manuscript.Rmd

---
title: "Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems"
output: 
  word_document:
    reference_docx: "word_format.docx"
  #pdf_document:
  #  latex_engine: xelatex
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: references.bib
csl: https://www.zotero.org/styles/ecosphere
mainfont: Times New Roman
header-includes:
  \usepackage{lineno, textgreek}
  \linenumbers
---

>>>>

---
title: "Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems"
output: 
  # word_document:
  #   reference_docx: "word_format.docx"
  pdf_document:
   latex_engine: xelatex
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: references.bib
csl: https://www.zotero.org/styles/ecosphere
mainfont: Times New Roman
header-includes:
  \usepackage{lineno, textgreek}
  \linenumbers
---
